### 2020-06-02 documents/Proof Response/proof_response.tex

@@

        \item TODO: Email E. Wolfe

@@

        \item Regarding figures 4, 5, 6 and 7, the incorrect figures were used in the proof. The discrepancy between the figure files and appearance in the submitted article were a result of using the a clipping/trimming option of \verb|\includegraphics| command of the \verb|graphicx| package in order to trim whitespace and superfluous figure titles. The usage of the this option is as follows:

@@

        Attached to this proof correction are ``corrected'' figure replacements for figures 4, 5, 6 and 7 which have the cropping already applied. As such, the figures should now appear correctly in the article and will match the figure files exactly. The figure files are respectively named:

@@

        \item[FQ.]

@@

            \item These private communications should be dated: November 2016 for [27] and August 2017 for both [41] and [42].

@@

    \textbf{Other Corrections to Address for This Paper:}
    \begin{itemize}
        \item The justification of items within Tables I and II are inconsistent.
        \item In equation (C1), the addition of the \verb|\times| is incorrect. The pertinent portion of equation (C1) is intended to be a comma separated list.
        \item Page 16 line 1097, there is a citation to [59] typo; the surrounding sentence should read ``A popular tool for linear quantifier elimination is Fourier-Motzkin elimination [21,55,58].'' with [59] omitted.
        \item Page 1 line 50, should read ``...inequalities can be understood as consequences...''. Currently, the word ``be'' is missing.
        \item Page 3 line 169, there is a math typo: the descendants of a node $\Delta[\mathcal{G}]n$ should be $\mathsf{De}_{\mathcal{G}}(n)$. Specifically, \verb|\mathsf{De}_{\mathcal{G}}(n)| produces the desired effect.
        \item Page 3 line 198, there is a typo in an inline equation. The surrounding sentence should read: ``...existence or non-existence of a set of causal parameters for $\mathcal G$ such that $P_{\mathcal{N}_{O}} = \sum_{n \not \in \mathcal{N}_{O}} P_{\mathcal{N}}$ where $P_{\mathcal{N}}$ is again given by Eq. (1). The complementary...''.
        \item Page 5 line 381, there is a small typo; ``variable'' should be ``variables''. The surrounding sentence should read: ``...crucial distinction is that $S_{A}$ and $S_{B}$ are random variables representing...''.
        % \item Page 6 line 472, ``Section VI'' should be ``Sec. VI'' to be consistent with the remainder of the document.
        \item Page 7 line 511, ``there'' should be omitted. ``Second, it is known that the inequalities...''.
        \item In several locations, the proof correctly replaces the usage of ``Section'' with its shorthand ``Sec.''. Should this correction also be applied to usage of ``Appendix'', i.e. ``Appendix'' becomes ``App.'' where applicable?
    \end{itemize}

>>>>

    \textbf{Attached Files:}
    \begin{itemize}
        \item {\verb|references.bib|} is a complete references file for the entire manuscript. Specifically, entries that required updating have been updated pursuant to the individual updates summarized below.
        \item Each of the four \verb|figure_*.pdf| files are explained in correction (7.) below:
    \end{itemize}

@@

        \item Currently, the publishing information for this reference is up-to-date.

@@

        \item Regarding figures 4, 5, 6 and 7, the incorrect figures were used in the proof. The discrepancy between the figure files and appearance in the submitted article were a result of using the a clipping/trimming option of \verb|\includegraphics| command of the \verb|graphicx| package in order to trim whitespace and superfluous figure titles. The usage of this option is as follows:

@@

        Nonetheless, attached to this proof correction are ``corrected'' figure replacements for figures 4, 5, 6 and 7 which have the cropping already applied. As such, the figures should now appear correctly in the article and will match the figure files exactly. The figure files are respectively named:

@@

        \item[FQ.] The funding information is both correct and complete.

@@

            \item The authors recommend that these private communications be dated: November 2016 for [27] and August 2017 for both [41] and [42].

@@

    \textbf{Other Comments to Address for This Paper:}
    \begin{itemize}
        \item The author's names and institution's names are all spelled correctly.
        \item The removal of the word ``of'' from the paper title is noted by the authors and approved.
        \item The justification of items within Tables I and II are inconsistent.
        \item In equation (C1), the addition of the \verb|\times| is incorrect. The pertinent portion of equation (C1) is intended to be a comma separated list.
        \item Page 16 line 1097, there is an inappropriate citation to [59]; the surrounding sentence should read ``A popular tool for linear quantifier elimination is Fourier-Motzkin elimination [21,55,58].'' with [59] omitted.
        \item Page 1 line 50, should read ``...inequalities can be understood as consequences...''. Currently, the word ``be'' is missing.
        \item Page 3 line 169, there is a math typo: the descendants of a node $\Delta[\mathcal{G}]n$ should be $\mathsf{De}_{\mathcal{G}}(n)$. Specifically, \verb|\mathsf{De}_{\mathcal{G}}(n)| produces the desired effect.
        \item Page 3 line 198, there is a typo in an inline equation. The surrounding sentence should read: ``...existence or non-existence of a set of causal parameters for $\mathcal G$ such that $P_{\mathcal{N}_{O}} = \sum_{n \not \in \mathcal{N}_{O}} P_{\mathcal{N}}$ where $P_{\mathcal{N}}$ is again given by Eq. (1). The complementary...''.
        \item Page 5 line 381, there is a small typo; ``variable'' should be ``variables''. The surrounding sentence should read: ``...crucial distinction is that $S_{A}$ and $S_{B}$ are random variables representing...''.
        % \item Page 6 line 472, ``Section VI'' should be ``Sec. VI'' to be consistent with the remainder of the document.
        \item Page 7 line 511, ``there'' should be omitted. ``Second, it is known that the inequalities...''.
        \item In several locations, the proof correctly replaces the usage of ``Section'' with its shorthand ``Sec.''. Should this correction also be applied to usage of ``Appendix'', i.e. ``Appendix'' becomes ``App.'' where applicable?
    \end{itemize}
